Analysis of Retrospective COVID-19 data

### 2020-10-04 manuscript/analysis_brms.Rmd
add 3-outcome categorical analysis

```{r}
data$patient_data <- data$patient_data %>%
  mutate(
    survival = outcome != "Death",
    discharged = outcome == "Discharged"
  )
```

@@

```{r}
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["competing_hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["competing_hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["competing_hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["competing_hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

>>>>

```{r}
data$patient_data <- data$patient_data %>%
  mutate(
    survival = outcome != "Death",
    discharged = outcome == "Discharged",
    outcome3 = fct_collapse(outcome, Discharged = c("Discharged", "Transferred")) %>%
      fct_relevel("Hospitalized", "Discharged", "Death")
  )
```

@@

```{r}
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

## Analysis: Hospitalized vs. Discharged vs. Death

### Basic Categorical model

```{r, results="hide"}
form_outcome_base <- bf(
  outcome3 ~ sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az +
    (1 | hospital_id),
  family = categorical("logit")
)

prior_outcome_base <- 
  prior(normal(0, 5), class = "b", dpar = "muDeath") +
  prior(normal(0, 5), class = "sd", dpar = "muDeath") +
  prior(normal(0, 5), class = "b", dpar = "muDischarged") +
  prior(normal(0, 5), class = "sd", dpar = "muDischarged")

fit_outcome_base <- brm(
  formula = form_outcome_base,
  data = data$patient_data,
  prior = prior_outcome_base,
  file = "models/fit_outcome_base"
)
fit_outcome_base <- add_criterion(fit_outcome_base, "loo")
```

```{r}
summary(fit_outcome_base)
# ce <- conditional_effects(fit_outcome_base)
# plot(ce, ask = FALSE)
```

```{r}
draws <- tidy_draws(fit_outcome_base)
hypothesis_res_list[["hcq_az_outcome_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```
